Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-12 talk/pepm2011/paper.tex
use nice macros

While we do not offer a formal proof of it, it should be relatively clear
that the algorithm presented above is sound: it works by delaying (and
often completely removing) some operations.  The algorithm runs in a
single pass over the list of operations.  We can check that altough
recursively lifting a static object is not a constant-time operation,
the algorithm only takes a total time linear in the length of the trace.
Moreover, it gives the ``best'' possible result within its constrains,
e.g.\ in term of the number of residual operations.  The
algorithm itself is not particularly complex or innovative; our focus is
rather that \emph{in the context of tracing JITs} it is possible to find a
simple enough algorithm that still gives the best results.

Note in particular that objects in category 1 (i.e.\ the ones that do
not escape) are completely removed; moreover, objects in category 2
(i.e.\ escaping) are still partially dealt with: if such an object
escapes later than its creation point, all the operations inbetween that
involve the object are removed.

>>>>

While we do not offer a formal proof of it, it should be relatively clear
that the algorithm presented above is sound: it works by delaying (and
often completely removing) some operations.  The algorithm runs in a
single pass over the list of operations.  We can check that altough
recursively lifting a static object is not a constant-time operation,
the algorithm only takes a total time linear in the length of the trace.
Moreover, it gives the ``best'' possible result within its constrains,
\eg in term of the number of residual operations.  The
algorithm itself is not particularly complex or innovative; our focus is
rather that \emph{in the context of tracing JITs} it is possible to find a
simple enough algorithm that still gives the best results.

Note in particular that objects in category 1 (\ie the ones that do
not escape) are completely removed; moreover, objects in category 2
(\ie escaping) are still partially dealt with: if such an object
escapes later than its creation point, all the operations inbetween that
involve the object are removed.
